\section{Introduction}
\label{sec:intro}

Distributed population-game and Nash-seeking methods have become a standard route
to coordinate large teams: agents adjust their strategies from locally
communicated aggregates, and the dynamics converge to an equilibrium of a
constrained potential game~\cite{sandholm2010population,quijano2017role,%
barreiro2016constrained,martinezpiazuelo2022}. Every one of these methods rests on
a silent premise: that the communication graph needed to \emph{compute} the
equilibrium is available while the equilibrium is being reached.

For a mobile robot team this premise is not innocent, because the agents that
compute the equilibrium are the same agents whose placement forms the network.
Consider a heterogeneous team recruited to move a load across a gap. A profile can
be productively optimal---delivering exactly the demanded wrench (force and
torque~\cite{murray1994manipulation})---and yet commit every robot to lifting, so
that no robot remains to relay, algebraic connectivity collapses, and the very
estimator that produced the profile loses its consensus channel. The equilibrium
destroys the means of its own computation.

\paragraph*{The self-referential gap}
The population-games literature treats the interaction graph as \emph{given}: a
constraint or resource external to the game~\cite{quijano2017role,%
barreiro2016constrained}. Connectivity-control and multi-robot task-allocation
work maintains algebraic connectivity $\lamtwo$ as a separate design
objective~\cite{fiedler1973,ghosh2006growing,zavlanos2011connectivity,%
choi2009cbba,prorok2017diversity}. Neither addresses the case where the graph is
an \emph{output} of the equilibrium's spatial composition. We adopt the
distributed population-game and generalized-Nash machinery of Sandholm and of
Barreiro-G\'omez, Quijano, and Mart\'inez-Piazuelo~\cite{sandholm2010population,%
quijano2017role,barreiro2016constrained,martinezpiazuelo2022}, and treat the
self-referential case in which the decision itself generates the graph that
machinery presupposes.

\paragraph*{Key observation}
The productive optimum pins down the aggregate but not the composition. Because
the team payoff couples only through population
aggregates~\cite{jensen2010aggregative}, the set of profiles achieving the optimal
aggregate is a positive-dimensional polytope (Theorem~\ref{thm:degeneracy}):
classical theory says how much service each task gets, not \emph{which types}
provide it. That undetermined composition is exactly the freedom we use to keep
the network alive.

\paragraph*{Contributions}
\begin{itemize}
\item \textbf{Composition degeneracy} (Theorem~\ref{thm:degeneracy}): the
productively optimal aggregate is unique, but the equal-payoff composition face
$\Emanifold$ has dimension $(T\!-\!1)(K\!-\!1)$.
\item \textbf{Self-sustaining existence} (Theorem~\ref{thm:existence}): with an
endogenous, position-induced Laplacian on $\Emanifold$, a self-sustaining
equilibrium exists iff $\Lammax=\max_{x\in\Emanifold}\lamtwo(\Lap(x))\ge\sigmastar$.
This is \emph{selection within a degenerate Nash face}, not an added constraint.
\item \textbf{Exact self-defeat threshold} (Theorem~\ref{thm:stability}): the
coupled strategy/consensus error is locally exponentially stable iff
$c\,\mF\,\lamtwo>\vt^2$, deriving $\sigmastar=\vt^2/(c\,\mF)$ rather than importing it.
\item \textbf{Infinitesimal-reward selection} (Prop.~\ref{prop:selection}) and a
distributed algorithm, validated by closed-loop simulation with rigid-load
transport and second-order unicycles---including emergent relay roles.
\end{itemize}
We name the resulting refinement the WISE equilibrium. \emph{A WISE equilibrium
can both execute itself and compute itself.}